---
title: "CCB Project Management"
author: "Theo Killian"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This document serves as a report on all of the requests received and projects
currently completed by the CCB bioinformatics platform.

## Projects

The CCB bioinformatics platform receives requests for bioinformatic assistance
on various projects. The section below explores the types and nature of these
requested projects.

```{r echo=FALSE, warning=FALSE, message=FALSE}
# library("kableExtra")
library("tidyverse")
library("lubridate")
library("readxl")
library("DT")
```

```{r warning=FALSE, message=FALSE}
path <- "~/Documents/tmp/ccb_project_management/"
ccb_proj_mgt <- read_excel(paste0(path, "/ccb_proj_mgt.xlsx"))
# View(ccb_proj_mgt)

ccb_proj_mgt %>%
  dplyr::select(-c(remarks)) %>%
  dplyr::mutate(date_request = as.Date(date_request)) %>% 
  DT::datatable()
```

## Project Statistics

Statistics on the CCB projects are generated to better help visualize the 
distributions of projects types and number of requests per lab.

### Histogram of Project Types

Below is a histogram of the types of projects that have been requested by 
members of labs at CCB.

```{r warning=FALSE, message=FALSE}
ccb_proj_mgt %>%
  ggplot(aes(x = project_type, fill = unique(ccb_proj_mgt$project_type))) +
  geom_bar(stat = "count", fill = rainbow(
    n = length(unique(ccb_proj_mgt$project_type)))) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90))
```

### Histogram of Project Subtypes

Below is a histogram of the subtypes of projects that have been requested by 
members of labs at CCB.

```{r warning=FALSE, message=FALSE}
ccb_proj_mgt %>%
  ggplot(aes(x = project_subtype, fill = unique(ccb_proj_mgt$project_subtype))) +
  geom_bar(stat = "count", fill = rainbow(
    n = length(unique(ccb_proj_mgt$project_subtype)))) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90))
```

### Histogram of Total Time Devoted to Projects

Below is a histogram that displays the rough time in hours devoted to each
project that has been requested by labs at CCB. Note "CCB" donates generate
infrastructure projects such as bulk RNAseq pipelines which will be used by
many labs. Red dotted line represents the theoretical maximum time available to
devote equally to each lab (i.e. 40 hours a week, multiplied by 48 weeks,
divided by 12 labs = approximately 180 hours available to service each lab per
year. This calculation includes time spent in meetings, etc. but does not
include time spent for general communally available infrastructure projects such
as omics pipelines.)

```{r warning=FALSE, message=FALSE}
ccb_temp1 <- ccb_proj_mgt
ccb_temp1 %>%
  dplyr::filter(lab == "Bergers/Lambrechts") -> pan_mouse
ccb_temp1 %>%
  dplyr::filter(!lab == "Bergers/Lambrechts") -> ccb_temp1
pan_hrs <- (pan_mouse$duration_hrs[1] / 2)
pan_mouse_1 <- pan_mouse
pan_mouse_2 <- pan_mouse
pan_mouse_1$lab[1] <- "Bergers"
pan_mouse_2$lab[1] <- "Lambrechts"
pan_mouse_1$duration_hrs <- pan_hrs
pan_mouse_2$duration_hrs <- pan_hrs
dplyr::bind_rows(pan_mouse_1, pan_mouse_2, ccb_temp1) -> ccb_temp2
ccb_temp2 %>% 
  dplyr::group_by(lab) %>%
  summarise(duration_hrs) %>% 
  ggplot() +
  geom_bar(mapping = aes(x = lab, y = duration_hrs), stat = "identity",
                         color = length(unique(ccb_temp2$lab)),
                         fill = rainbow(n = length(ccb_temp2$lab))) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90)) +
  geom_hline(yintercept = 180, linetype = "dotted", color = "red")
```

### Project Timeline

Below is a histogram that displays the number of projects requested per month
for the period between August 2020 and February 2021.

```{r}
ccb_proj_mgt %>%
  dplyr::mutate(months = months(as.POSIXlt(date_request, format = "%Y%m%d"))) %>%
  dplyr::mutate(months = factor(months, levels = unique(months))) %>%
  group_by(months) -> ccb_month
ccb_month %>%
  ggplot(aes(x = months, color = months, fill = months)) +
    geom_bar(stat = "count") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 90))
```

```{r}
sessionInfo()
```
